\documentclass[10pt,twocolumn]{article}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amsmath, amssymb}
\usepackage[colorlinks=true, linkcolor=black, citecolor=black, urlcolor=black]{hyperref}

\title{\textbf{Project Title}}
\author{
    Zachary Caterer$^{1,2,3}$ \\
    \small $^1$Department of Computer Science, University of Colorado Boulder \\
    \small $^2$Department of Chemical and Biological Engineering, University of Colorado Boulder \\
    \small $^3$Interdisciplinary Quantitative Biology Program, University of Colorado Boulder
}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This is the abstract of the project proposal. It should provide a brief summary of the project, including the main objectives and expected outcomes.
\end{abstract}

\section{Introduction}
The introduction should provide background information on the topic, explain the motivation for the project, and outline the main goals and objectives.

\section{Related Work}
This section should review relevant literature and previous work in the field. Discuss how your project builds on or differs from existing research.

\section{Proposed Methodology}
Describe the methods and techniques you plan to use to achieve the project objectives. Include any specific algorithms, tools, or data sources you will use.

\section{Expected Results}
Outline the expected outcomes of the project. Discuss any hypotheses or predictions you have and how you will evaluate the success of the project.

\section{Timeline}
Provide a timeline for the project, including key milestones and deadlines.

\section{Conclusion}
Summarize the main points of the proposal and reiterate the significance of the project.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
